### 2017-02-26 thesis/thesis.tex
tmp commit
Finished the last bit of results1 - tmp commit

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttable}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{bm}                                % package for scientific notations and units

@@

% Make siunitx detect bold/italics/etc:
\sisetup{detect-weight=true,detect-family=true,detect-inline-weight=text,table-parse-only}

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
\includeonly{{./methods/methods},{./results/results},{./results/results2},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./misc/appendix}}

>>>>

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttable}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

% Make siunitx detect bold/italics/etc:
\robustify\bfseries
\sisetup{detect-all}

% Set the width of captions for threeparttable to \linewidth:
\captionsetup[threeparttable]{width=\linewidth}

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
\includeonly{{./methods/methods},{./results/results},{./results/results2},{./discussion/discussion},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./discussion/discussion},{./misc/appendix}}
